Oregon_Wildfire_reduced

### 2017-03-01 r_scripts/oregon_clean.rmd

```{r}
library(dplyr)
library(data.table)
library(knitr)
library(readxl)
getwd()

@@

>>>>

```{r}
library(dplyr)
library(data.table)
library(knitr)
library(readxl)
library(ggplot2)
getwd()

@@

## How many visits does unique personkey have?
```{r}
# pick up personkey and claim id column, make new column of unique number of visit
visit2 <- oregon_df %>%
  select(personkey, clmid) %>%
  distinct(clmid,personkey) %>%
  select(personkey, clmid) %>%
  group_by(personkey) %>%
  summarise(num_visit=n())

visit3 <- visit2 %>%
  group_by(num_visit) %>%
  summarise(n = n()) %>%
  mutate(total_n =sum(n),
  percent = round(n/total_n, 4)*100) %>% 
  select(num_visit, n, percent)

m <- cbind(sum(visit2$num_visit)/n_distinct(oregon_df$personkey), median(visit2$num_visit), max(visit2$num_visit))
colnames(m) <- c("Mean", "Median", "Max")

knitr::kable(m, align = "c", caption = "Statistics")

hist(visit3$num_visit, freq = T, xlab = "number of visit", main = "Visiting number for each personkey")
